Treebeard : A Compiler for Decision Forest Inference

### 2022-04-12 docs/MICRO 2022/main.tex
Add tiling section

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\scriptsize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

@@

%%%%%% -- PAPER CONTENT STARTS-- %%%%%%%%
\input{abstract}
\input{introduction}
\input{overview}

>>>>

\lstdefinestyle{c++}{language=C++,
    morekeywords={ensemble, getTree, getRoot, isLeaf, traverseTreeTile, getLeafValue, loadThresholds, loadFeatureIndices, loadTileShape, getChildNode},    
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\scriptsize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=c++}

@@

%%%%%% -- PAPER CONTENT STARTS-- %%%%%%%%
\input{abstract}
\input{introduction}
\input{overview}
\input{details}

### 2022-04-12 docs/MICRO 2022/overview.tex
Add tiling section

\subsection{Mid Level IR}
The Mid Level IR makes the loop structures and tree walks more explicit. Firstly, the order in which the iteration space of trees and inputs is walked is explicitly specified in the IR through loop nests. Also, tree specific operations such as \texttt{isLeaf}, \texttt{traverseTile}, \texttt{getLeafValue} are introduced so that the traversal of trees explicitly represented. The following listing shows the IR for inference using a model with four trees on an input batch with two rows. The listed IR walks all trees for one input row before moving to the next row. One important point to note here is that details such as the data structure used for the trees are not explicitly encoded in the IR. This allows us to reuse optimization and lowering passes on this level of the IR regardless of what the final in memory representation of the model is.

\begin{lstlisting}[language=C++]
  // Constant that represents the model being compiled
  forest = ensemble(...)
  for i = 0 to 2 step 1 {
    prediction = 0
    for t = 0 to 4 step 1 {
      tree = getTree(forest, t) 
      node = getRoot(tree)
      while (isLeaf(tree, n)==false)  do {
        node = traverseTreeTile(tree, node, rows[i])
      }
      treePrediction = getLeafValue(tree, node)
      prediction = prediction + treePrediction
    }
    predictions[i] = prediction
  }
\end{lstlisting}

>>>>

\subsection{Mid Level IR}
The Mid Level IR makes the loop structures and tree walks more explicit. Firstly, the order in which the iteration space of trees and inputs is walked is explicitly specified in the IR through loop nests. Also, operations such as \texttt{isLeaf}, \texttt{traverseTile}, \texttt{getLeafValue} are introduced so that the traversal of trees explicitly represented. The following listing shows the IR for inference using a model with four trees on an input batch with two rows. The listed IR walks all trees for one input row before moving to the next row. One important point to note here is that details such as the data structure used for the trees are not explicitly encoded in the IR. This allows us to reuse optimization and lowering passes on this level of the IR regardless of what the final in memory representation of the model is.

\begin{lstlisting}[style=c++]
  // Constant that represents the model being compiled
  forest = ensemble(...)
  for i = 0 to 2 step 1 {
    prediction = 0
    for t = 0 to 4 step 1 {
      tree = getTree(forest, t) 
      node = getRoot(tree)
      while (isLeaf(tree, n)==false)  do {
        node = traverseTreeTile(tree, node, rows[i])
      }
      treePrediction = getLeafValue(tree, node)
      prediction = prediction + treePrediction
    }
    predictions[i] = prediction
  }
\end{lstlisting}
